Weather Data Integration and Assimilation System\\

### 2020-02-11 lit/sec_1-fews.tex
Updates from Overleaf
After 2nd review

There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even for drought.
Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems. Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
This chapter \ref{ch:literature} presents a Literature review on existing systems and their architecture approach and design with available resources.
In Section \ref{se:fews}, we present most influenced systems for \acrshort{wdias} is \acrshort{fews}. \acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in Section \ref{se:lead}. \acrshort{lead} is following the \acrfull{soa} for system architecture. In Section \ref{se:dias}, we discussed about \acrfull{dias} which is developed by Japanese, and support as a common data platform other than weather data. \acrfull{madis} is another widely use data integration system, which also provide data access with quality control, and we discuss in the last Section \ref{se:madis}.
Under each system we explore both system architecture, scalability and flexibility of the system.

@@

In figure \ref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems. The widely using concept is using meteorological forecast data to get precipitation and, then using hydrological and hydraulic model chain to predict the level affect on the ground. The hydrological and hydraulic model should be design based on the ground. Basically ground should be analyze geographically and divide into the catchments. Based on the affected catchment, it can be further divide into sub areas in order to reduce the complexity of the simulation task. Ideally the forecasting system should therefore be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.

@@

Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g., the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}. This gives an opportunity to index the data base on above key fields and store the data separately, in order to take the advantage of putting multiple data resources into the system. As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on source such as external source or hydrological model of which the time series are a result. Or separate by data type and store in multiple storage give the capability for the system to scale with factor of identical types that can be identified. Example of separation by data types of scalar, vector and gridded will increase the scaling factor by 3x.

Data processing and manipulation is a required process in weather forecasting. Most of the data that is imported from external sources is not at the appropriate temporal and spatial scale to be applied as an input to a forecasting model, or to be used directly in product generation. As a consequence, generic data processing steps form the predominant effort in most applications of models in the forecast environment. Some examples include data validation, serial and spatial interpolation, aggregation and dis-aggregation, and merging data \cite{Werner2013TheSystem}. This a vital feature in a forecasting system, and affect on the quality and accuracy of the predicted data outputs. Because of the common data model concept in the \acrshort{fews}, data processing via these function is much effective. The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the application programming interface (API). It obvious that for additional feature integration, user should implement the new functional extensions via Java programming language. Users does not have the flexibility of develop with some other languages they are familiar with or use the support from another language. As an example, Python language is easy to use for beginners and many of data scientists are using this programming language for development and it has many data available libraries for data processing. But in the \acrshort{fews} users do not ave the capability to take the advantage of such existing things.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{lit/fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.png}
    \caption[Architecture of \acrshort{fews}]{Architecture of \acrshort{fews} \cite{Werner2013TheSystem}.}
    \label{fi:fews_data_layer}
\end{figure}
Most of the library of functions provided work equally on scalar and gridded time series. As with all other modules this communicates with the database solely through the data access layer as shown in \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}. As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection. It is possible to setup and connect to a enterprise level database with clustering and shading as a paid solution, in order to serve many requests as possible. But the design it self inherently suffer with the database bottleneck which effected on running a large set of timeseries or models.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{lit/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.png}
    \caption[Linking \acrshort{fews} with external models]{Linking \acrshort{fews} with external models \cite{Werner2013TheSystem}.}
    \label{fi:fews_general_adapter}
\end{figure}
On of the simple and most effective feature in the \acrshort{fews} is open approach to integration of models and data. This approaches the concept of the open modeling framework proposed by \cite{Kokkonen2003InterfacingXML}. It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
\acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model; and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step. \acrshort{fews} subsequently imports the results into the database from the XML files (see Figure \ref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}. The process is simple and consistence through out all the model integration. The model execution is done by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system. Users does not have the flexibility to run the models with different configurations such as running with parallel execution. That may be overcome by triggering a external process at the execution time, but it introducing more difficulty for handling after model executed successfully, preceding to the next step in the process. This part of the system feature is not focus on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system. But it is a concept that need to be discuss and understand properly in order to design a data integration and assimilation system.

Exchanging data with the model is primarily through XML files. In some cases these XML files may become very large, which may lead to I/O bottlenecks and subsequent performance issues \cite{Werner2013TheSystem}. This issue is thoroughly discussed previous paragraphs and the authors of the \cite{Werner2013TheSystem} seems to be notice and accept it here. For overcome this issue they introduced the file-based exchange of data. This includes the use of binary-XML files, streaming files through memory, and the use of \acrshort{netCDF} files. But far as for users it seems to be adding more complexity and context in order to get higher performance via the system.

If particular adapter for a model is not present in the list of \acrshort{fews} adapter, user has the flexibility to implement an adapter for it. The effort of developing an adapter for a model code not previously integrated with \acrshort{fews} will vary depending on the complexity of the model I/O formats \cite{Werner2013TheSystem}. If user wants to use existing adapter and need to configure something not supported via the existing adapter, it is hard to get done. Also there are some cases it is hard to develop an adapter or running alongside with the \acrshort{fews}. As an example FLO2D model is using for hydrologic modeling and the model is only support only on Windows based operating systems. If you setup the system on Linux base operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
The final step and one of important feature is exporting the data from the system in useful manner.
The forecasting process is often a sequence of steps, starting with the import of data, a number of data processing and modeling steps, and culminating in the generation of products to be disseminated to the warning process. This is supported via the work flow process in the \acrshort{fews}. The scope of the \acrshort{wdias} is not focus on adding such a feature in the system, rather user have to use scientific work flow management system or come up with own version of work flow.

When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g.,the lead time of the forecast) before moving on to the next step. This precludes tightly coupling of models, even explicitly \cite{Werner2013TheSystem}. As it mentioned above, users can run multiple models parallel or run those sequentially as needed.

>>>>

Several weather forecasting, assimilation, and dissemination systems are developed to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even droughts. %Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems. 
Other countries are also using those systems while adopting them %with own version of system which effective for the 
to specific weather condition.% in a particular country.
This chapter presents a literature review on existing systems and their architecture approach and design. In Section \ref{se:fews}, we present \acrshort{fews}. \acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in Section \ref{se:lead}. % \acrshort{lead} is following the \acrfull{soa} for system architecture. 
In Section \ref{se:dias}, we discussed about \acrfull{dias} which is a common data platform that can work with weather data. \acrfull{madis} is another widely use data integration system, which also provide data access with quality control, whihc we discuss in Section \ref{se:madis}.
Under each system we explore both system architecture, scalability, and flexibility of the system.

@@

In \db{Figure} \ref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems. The widely using concept is using meteorological forecast data to get precipitation and, then using hydrological and hydraulic model chain to predict the level affect on the ground. The hydrological and hydraulic model should be design based on the ground. Basically ground should be analyze geographically and divide into the catchments. Based on the affected catchment, it can be further divide into sub areas to reduce the complexity of the simulation task. Ideally the forecasting system should therefore be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.
\dbc{F is capital and T is capital when referring to Figures and Tables. Fix all other places.}

@@

Given above drawback on storing the data in the system, within the \acrshort{fews} data model, time series are uniquely identified by their location and data type, as well as an id related to the source of the data (e.g., the external source or hydrological model of which the time series are a result) \cite{Werner2013TheSystem}. This gives an opportunity to index the data base on above key fields and store the data separately, to take the advantage of putting multiple data resources into the system. As an example, instead of storing the data at a single timeseries table, it is possible to separate and index the database based on source such as external source or hydrological model of which the time series are a result. Or separate by data type and store in multiple storage give the capability for the system to scale with factor of identical types that can be identified. Example of separation by data types of scalar, vector and gridded will increase the scaling factor by 3x.

Data processing and manipulation is a required process in weather forecasting. Most of the data that is imported from external sources is not at the appropriate temporal and spatial scale to be applied as an input to a forecasting model, or to be used directly in product generation. As a consequence, generic data processing steps form the predominant effort in most applications of models in the forecast environment. Some examples include data validation, serial and spatial interpolation, aggregation and dis-aggregation, and merging data \cite{Werner2013TheSystem}. This a vital feature in a forecasting system, and affect on the quality and accuracy of the predicted data outputs. Because of the common data model concept in \acrshort{fews}, data processing via these function is much effective. The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the {application programming interface (API)}. It is obvious that for additional feature integration, user should implement the new functional extensions via Java programming language. Users does not have the flexibility of develop with some other languages they are familiar with or use the support from another language. As an example, Python language is easy to use for beginners and many of data scientists are using this programming language for development and it has many data available libraries for data processing. But in \acrshort{fews}, users do not ave the capability to take the advantage of such existing things.
\dbc{Define Abb. for API in Chapter 1.}

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{lit/fews/Architecture-of-Delft-FEWS-showing-the-data-base-the-data-access-layers-and-examples-of_W640.png}
    \caption[Architecture of \acrshort{fews}]{Architecture of \acrshort{fews} \cite{Werner2013TheSystem}.}
    \label{fi:fews_data_layer}
\end{figure}
Most of the library of functions provided work equally on scalar and gridded time series. As with all other modules this communicates with the database solely through the data access layer as shown in \db{Section} \ref{fi:fews_data_layer} \cite{Werner2013TheSystem}. As it shown in the figure, it is clearly showing that, the system is depends on single database and via the data access layer all the requests are coming to the database though a connection. It is possible to setup and connect to a enterprise level database with clustering and shading as a paid solution, to serve many requests as possible. But the design it self inherently suffer with the database bottleneck which effected on running a large set of timeseries or models.
\dbc{When referring to a section you need to use the word "Section" as highlighted above. Fix all other places.}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{lit/fews/Linking-Delft-FEWS-with-external-models-The-fi-gure-shows-the-fl-ow-of-data-through-XML_W640.png}
    \caption[Linking \acrshort{fews} with external models]{Linking \acrshort{fews} with external models \cite{Werner2013TheSystem}.}
    \label{fi:fews_general_adapter}
\end{figure}
On of the simple and most effective feature in the \acrshort{fews} is open approach to integration of models and data. This approaches the concept of the open modeling framework proposed by \cite{Kokkonen2003InterfacingXML}. It simply gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new integration flows as much as possible.
\acrshort{fews} generates the input data as a set of XML files to a defined location; an adapter developed specifically for the model in question transforms this to the required native format in a pre-processing step; \acrshort{fews} executes the model; and the adapter to that model then converts the native formatted results into XML formatted files in a post processing step. \acrshort{fews} subsequently imports the results into the database from the XML files (see Figure \ref{fi:fews_general_adapter}) \cite{Werner2013TheSystem}. The process is simple and consistence through out all the model integration. The model execution is done by the \acrshort{fews} or the model adapter which is causing tide coupling into the execution process in the system. Users does not have the flexibility to run the models with different configurations such as running with parallel execution. That may be overcome by triggering a external process at the execution time, but it introducing more difficulty for handling after model executed successfully, preceding to the next step in the process. This part of the system feature is not focus on the \acrshort{wdias} and user has to come up with own flow or use existing scientific flow management system. But it is a concept that need to be discuss and understand properly to design a data integration and assimilation system.

Exchanging data with the model is primarily through XML files. In some cases these XML files may become very large, which may lead to I/O bottlenecks and subsequent performance issues \cite{Werner2013TheSystem}. This issue is thoroughly discussed previous paragraphs and the authors of the \cite{Werner2013TheSystem} seems to be notice and accept it here. For overcome this issue they introduced the file-based exchange of data. This includes the use of binary-XML files, streaming files through memory, and the use of \acrshort{netCDF} files. But far as for users it seems to be adding more complexity and context to get higher performance via the system.

If particular adapter for a model is not present in the list of \acrshort{fews} adapter, user has the flexibility to implement an adapter for it. The effort of developing an adapter for a model code not previously integrated with \acrshort{fews} will vary depending on the complexity of the model I/O formats \cite{Werner2013TheSystem}. If user wants to use existing adapter and need to configure something not supported via the existing adapter, it is hard to get done. Also there are some cases it is hard to develop an adapter or running alongside with the \acrshort{fews}. As an example FLO2D model is using for hydrologic modeling and the model is only support only on Windows based operating systems. If you setup the system on Linux base operating system and using Linux based models, it is hard for users to come up with a solution for integrating the FLO2D models.
The final step and one of important feature is exporting the data from the system in useful manner.
The forecasting process is often a sequence of steps, starting with the import of data, a number of data processing and modeling steps, and culminating in the generation of products to be disseminated to the warning process. This is supported via the work flow process in \acrshort{fews}. The scope of the \acrshort{wdias} is not focus on adding such a feature in the system, rather user have to use scientific work flow management system or come up with own version of work flow.

When running sequential steps within a work flow in \acrshort{fews}, each step is run for the full time window required (e.g., the lead time of the forecast) before moving on to the next step. This precludes tightly coupling of models, even explicitly \cite{Werner2013TheSystem}. As it mentioned above, users can run multiple models parallel or run those sequentially as needed.

### 2020-02-11 lit/sec_3-other-systems.tex
After 2nd review

The mechanism of storing data in \acrshort{dias}, similar to the other systems discussed.
These data sets are stored in an extra large volume disk array system with API (Application Programming Interface) software used to import the data. APIs work to convert or re-format data into manageable forms and are useful in creating the DIAS storage archive. API software consists of several tools, including the "Real-time data crawling and archiving system", "Data upload system", "Quality control system", and "Metadata management system" \cite{Kawasaki2018DataReduction}. In order to store on the large volume of disk space, it convert the data via provided set of APIs. This can be consider same as the open data model provide by the \acrshort{fews}. Other than that, \acrshort{dias} consist of additional tools which provide the functionality of quality control of the data, and metadata management which is similar to some of services in \acrshort{lead}.

As shown in figure \ref{fi:dias_common_platform}, it provides an application layer which allows domain scientists to working on research tasks, and to develop specific tools and applications by working together with Information Technology experts. \cite{Kawasaki2018DataReduction}. Once the data is achieved on the \acrshort{dias} system, it share those details via Shared API layer. Thus it allows users to remote access to the data, and easy integration via the APIs.

@@

\acrshort{madis} comprises a distributed architecture for ingest, processing, and data distribution functions.
In addition, in a recent architectural advance, the various functional hosts are arranged in pairs using High-Availability (HA) Linux to provide auto mated failover in case of system failure. Real-time data distribution methods include FTP, Local Data Manager (LDM), and the Web-based OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ARCHITECTUREP2.39}. As it mentioned above, the \acrshort{madis} is implemented based on a distributed architecture which is available at the time of it's development. Even it is not clear mentioned, it is using functional call like Remote procedure call (RPC) in order to invoke among a cluster of nodes as shown in figure \ref{fi:madis_flow}. In order to get High Availability, it has added some update to it's architecture. The conclusion of this statement is, these kind of functionalities are available at the modern the Cloud Computing tools, and out of the box those tools are providing the scalability and high availability. Using those tools, it possible to implement a such system with less effort and high confidence.

@@

Most of the above systems develop by many developers and researcher via many of funding. And most of them are depend on underline platform, and not up to date with the modern technologies such as Cloud Computing.

>>>>

The mechanism of storing data in \acrshort{dias}, similar to the other systems discussed.
These data sets are stored in an extra large volume disk array system with API (Application Programming Interface) software used to import the data. APIs work to convert or re-format data into manageable forms and are useful in creating the DIAS storage archive. API software consists of several tools, including the real-time data crawling and archiving system, data upload system, quality control system, and metadata management system \cite{Kawasaki2018DataReduction}. To store on the large volume of disk space, it convert the data via provided set of APIs. This can be consider same as the open data model provide by the \acrshort{fews}. Other than that, \acrshort{dias} consist of additional tools which provide the functionality of quality control of the data, and metadata management which is similar to some of services in \acrshort{lead}.

As shown in figure \ref{fi:dias_common_platform}, it provides an application layer which allows domain scientists to working on research tasks, and to develop specific tools and applications by working together with Information Technology experts \cite{Kawasaki2018DataReduction}. Once the data is achieved on the \acrshort{dias} system, it share those details via Shared API layer. Thus it allows users to remote access to the data, and easy integration via the APIs.

@@

\dbc{In Fig. 2.8, is it the data flow?}

\acrshort{madis} comprises a distributed architecture for ingest, processing, and data distribution functions.
In addition, in a recent architectural advance, the various functional hosts are arranged in pairs using High-Availability (HA) Linux to provide auto mated failover in case of system failure. Real-time data distribution methods include FTP, Local Data Manager (LDM), and the Web-based OPeNDAP (OPen source project for Network Data Access Protocol) \cite{Macdermaid2005ARCHITECTUREP2.39}. As it mentioned above, the \acrshort{madis} is implemented based on a distributed architecture which is available at the time of it's development. Even it is not clear mentioned, it is using functional call like Remote Procedure Call (RPC) to invoke among a cluster of nodes as shown in figure \ref{fi:madis_flow}. To get high availability, it has added some update to it's architecture. The conclusion of this statement is, these kind of functionalities are available at the modern the Cloud Computing tools, and out of the box those tools are providing the scalability and high availability. Using those tools, it possible to implement a such system with less effort and high confidence.

@@

Most of the above systems develop by many developers and researcher via many of funding. And most of them are depend on underline platform, and not up to date with the modern technologies such as cloud computing.

### 2020-02-11 method/sec_0_introduction.tex
Misc fixes on references
After 2nd review

This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}, then how is it trying to propose a better system with overcoming the issues.
In the section \ref{se:high_level_design}, it give a brief disussion on how the weather forecasting is happening, and why it need to interact with multiple data formats.
Then following subsections define few termelogy which are using in the \acrshort{wdias}, and scope of the thesis.
Following section \ref{se:architectural_decisions} that we evolve over while designing and implementing the \acrshort{wdias}.
The section \ref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
Then the reason behind developing Heirarchital Database and technologies use for that discussed in the section \ref{se:db_struct}.
Throw out the section \ref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
Last section \ref{se:query} includes details on how to perform timeseries search and geo based queries.

@@

In order to get overall idea on the flow of weather prediction, lets look into one of flows using in \acrshort{curw} \cite{CUrWSL2017SL}.
\begin{itemize}
    \item Extract GRIB WRF model data to netCDF
    \item From netCDF to CSV of each location data, then feed to HEC-HMS and get the output as CSV
    \item CSV + Rain cell Grid feed into the FLO2D, and get the water level as Grid ASCII files after completion of simulation
    \item Upload ASCII files to ArcGIS create Raster files, then use for the LOSS Estimation
\end{itemize}
When looked into the above flow, it clear understanding on multiple data formats using while weather predictions.
Other than that, in order to correct the model outputs, it required to collect real time data such as;
\begin{itemize}
    \item Automated weather station sending data in higher frequent intervals via HTTP protocol
    \item Automated water level stations send data in higher frequency
\end{itemize}
Other than above there are many data formats using for handling data based on devices and standards which are using. Also for data modeling, it needs to convert the data into model compatible data format, then after successfully run the model it needs to collect data from the model output data formats.

\subsection{Modules of Weather Data Integration System}
\label{subse:modules_weather_data_integration_sys}

The figure \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/misc/weather_data_system_components.jpg}}
\caption{Components of a weather data system.}
\label{fi:wdia_components}
\end{figure}
\subsubsection{Integration}
The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally. 
\subsubsection{Assimilation}
Then the system should be able to fulfill weather models varying data requirements. Also those models reproduce large set of redundant data, thus system should store the bulk data while optimizing the disk space.
\subsubsection{Dissemination}
Then different users should be able to retrieve data as they required. Also the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.

\subsubsection{Timeseries}
A timeseries is simply a series of data points ordered in time. In weather domain, it interest in timeseries in perspective of observations to forecasting.
Each timeseries, the data points can be form in different formats as well.
\begin{itemize} 
    \item Scalar - 0D
    \item Vector - 1D
    \item Grid - 2D
    \item Polygon - 2D
\end{itemize}

@@

\subsubsection{Base of WDIAS architecture}
The base of WDIAS architecture origins based on attributes of a timeseries. There are many attributes to differentiate timeseries one from another. But following can be consider as key attributes to uniquely identify a timeseries from another for the \acrshort{wdias}. In detail description available at the section \ref{se:db_struct}.
\begin{itemize}
    \item Module - module that generate the timeseries
    \item Value Type - Scalar, Vector, Grid, Polygon
    \item Location 
    \item Parameter - measuring parameter of timeseries
    \item Timeseries type
    \begin{itemize}
        \item sources - External, Simulated
        \item category - Historical, forecast
    \end{itemize}
    \item Time step
\end{itemize}

>>>>

This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}. %, then how is it trying to propose a better system with overcoming the issues.
In Section \ref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it need to interact with multiple data formats is presented. Then following subsections define few termelogy which are using in the \acrshort{wdias}, and scope of the thesis.
Section \ref{se:architectural_decisions} that we evolve over while designing and implementing the \acrshort{wdias}.
The section \ref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
Then the reason behind developing Heirarchital Database and technologies use for that discussed in the section \ref{se:db_struct}.
Throw out the section \ref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
Finally, in Section \ref{se:query} includes details on how to perform timeseries search and geo based queries.

@@

To get overall idea on the flow of weather prediction, let us look into one of flows using in \acrshort{curw} \cite{CUrWSL2017SL}.
\dbc{Use CUrW-SL}

\begin{enumerate}
    \item Extract GRIB WRF model data to netCDF
    \item From netCDF to CSV of each location data, then feed to HEC-HMS and get the output as CSV
    \item CSV and Rain cell Grid feed into the FLO2D, and get the water level as Grid ASCII files after completion of simulation
    \item Upload ASCII files to ArcGIS create Raster files, then use for the LOSS Estimation
\end{enumerate}
When looked into the above flow, it clear understanding on multiple data formats using while weather predictions.
Other than that, to correct the model outputs, it required to collect real time data such as;
\begin{itemize}
    \item Automated weather station sending data in higher frequent intervals via HTTP protocol
    \item Automated water level stations send data in higher frequency
\end{itemize}
Other than above there are many data formats using for handling data based on devices and standards which are using. Also, for data modeling, it needs to convert the data into model compatible data format, then after successfully run the model it needs to collect data from the model output data formats.

\subsection{Modules of Weather Data System}
\label{subse:modules_weather_data_integration_sys}

Figure \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system which consists of the following modules:
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\textwidth]{method/misc/weather_data_system_components.jpg}}
\caption{Components of a weather data system.}
\label{fi:wdia_components}
\end{figure}

\paragraph{Integration}-- The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally. 
\subsubsection{Assimilation}
Then the system should be able to fulfill weather models varying data requirements. Also those models reproduce large set of redundant data, thus system should store the bulk data while optimizing the disk space.
\paragraph{Dissemination}-- Then different users should be able to retrieve data as they required. Also the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.

\paragraph{Timeseries}-- A timeseries is simply a series of data points ordered in time. In weather domain, it interest in timeseries in perspective of observations to forecasting. Each timeseries, the data points can be form in different formats as well. For example, Scalar (0D), Vector (1D), Grid (2D), and Polygon (2D).

@@

\subsubsection{Base of WDIAS architecture}
\dbc{What's Base of WDIAS architecture?}
The base of WDIAS architecture origins based on attributes of a timeseries. There are many attributes to differentiate timeseries one from another. But following can be consider as key attributes to uniquely identify a timeseries from another for the \acrshort{wdias}. In detail description available at the section \ref{se:db_struct}.
\begin{itemize}
    \item Module -- module that generate the timeseries
    \item Value type -- Scalar, Vector, Grid, Polygon
    \item Location 
    \item Parameter -- measuring parameter of timeseries
    \item Timeseries type
    \begin{itemize}
        \item sources -- External, Simulated
        \item category -- Historical, forecast
    \end{itemize}
    \item Time step
\end{itemize}
\dbc{Use bullets only when essential. Other places use paragraphs.}

### 2020-02-11 results/sec_2-workload.tex
Caption top of table
After 2nd review

\begin{table}[ht]
\footnotesize
\begin{tabular}{lccccl}
\hline
\multicolumn{1}{c}{\textbf{Node Label}} & \textbf{vCPU} & \textbf{RAM (GB)} & \textbf{Storage (GB)} & \textbf{Quantity} & \multicolumn{1}{c}{\textbf{EC2 Name}} \\ \hline
core & 16 & 32 & 15 & 1 & c5.4xlarge \\
grid & 8 & 16 & 25 & 1 & c5.2xlarge \\
scalar & 8 & 16 & 20 & 1 & c5.2xlarge \\
test & 4 & 10.5 & 5 & 1 & c5n.xlarge \\ \hline
\end{tabular}
\caption{\acrshort{eks} nodes}
\label{tab:aws_eks_nodes}
\end{table}

@@

\dbc{- e.g., diagram indicating the nodes and their connectivity (load generator, target, storage, etc.), Then briefly describe the diagram.}

Users can use one of above features to fine-tune the \acrshort{wdias} to perform better. For the moment, \acrshort{wdias} helm charts uses node Affinity in order to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes. Pods are assigned to the nodes \ref{tab:aws_eks_nodes} based on the node label as below;
\begin{itemize}
    \item \emph{core}: metadata, extensions, query, status and extension services
    \item \emph{grid}: grid adapter, import and export grid data
    \item \emph{scalar}: scalar and vector adapters, import and export of same data types
    \item \emph{test}: jmeter and metric server
\end{itemize}
The databases uses for data consistency and performance in storage optimization with search capabilities. But because of that, it only possible to run one instance of those. In the \acrshort{wdias}, the MySQL and MongoDb are not getting higher load as adapter databases such as InfluxDB for scalar and vector data types, and netCDF for grid data type. In order to keep up with the pace, those microservice pods are assign to dedicated nodes in order to increase the performance of inter-service communication.

>>>>

\begin{table}[ht]
\caption{\acrshort{eks} nodes}
\footnotesize
\begin{tabular}{lccccl}
\hline
\multicolumn{1}{c}{\textbf{Node Label}} & \textbf{vCPU} & \textbf{RAM (GB)} & \textbf{Storage (GB)} & \textbf{Quantity} & \multicolumn{1}{c}{\textbf{EC2 Name}} \\ \hline
core & 16 & 32 & 15 & 1 & c5.4xlarge \\
grid & 8 & 16 & 25 & 1 & c5.2xlarge \\
scalar & 8 & 16 & 20 & 1 & c5.2xlarge \\
test & 4 & 10.5 & 5 & 1 & c5n.xlarge \\ \hline
\end{tabular}
\label{tab:aws_eks_nodes}
\end{table}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{results/work_load/eks_node_setup.jpg}
    \caption{\acrfull{eks} node setup}
    \label{fi:eks_node_setup}
\end{figure}

Users can use one of above features to fine-tune the \acrshort{wdias} to perform better. For the moment, \acrshort{wdias} helm charts uses node Affinity in order to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes. Pods are assigned to the nodes \ref{tab:aws_eks_nodes} based on the node label as below;
\begin{itemize}
    \item \emph{core}: metadata, extensions, query, status and extension services
    \item \emph{grid}: grid adapter, import and export grid data
    \item \emph{scalar}: scalar and vector adapters, import and export of same data types
    \item \emph{test}: jmeter and metric server
\end{itemize}
Figure \ref{fi:eks_node_setup} show the overview of show the nodes are setup and each microservices are assigned to each node, the connectivity of the nodes, and the data interactions via the arrows.
The databases uses for data consistency and performance in storage optimization with search capabilities. But because of that, it only possible to run one instance of those. In the \acrshort{wdias}, the MySQL and MongoDb are not getting higher load as adapter databases such as InfluxDB for scalar and vector data types, and netCDF for grid data type. In order to keep up with the pace, those microservice pods are assign to dedicated nodes in order to increase the performance of inter-service communication.
